Random Forest | Ques 10.1

### 2022-09-28 hw5-1/ashish/a.0_random_forest.Rmd
submission RF v0

| Variable | Description                                                                            |
|-----------------|-------------------------------------------------------|
| M        | percentage of males aged 14--24 in total state population                              |
| So       | indicator variable for a southern state                                                |
| Ed       | mean years of schooling of the population aged 25 years or over                        |
| Po1      | per capita expenditure on police protection in 1960                                    |
| Po2      | per capita expenditure on police protection in 1959                                    |
| LF       | labour force participation rate of civilian urban males in the age-group 14-24         |
| M.F      | number of males per 100 females                                                        |
| Pop      | state population in 1960 in hundred thousands                                          |
| NW       | percentage of nonwhites in the population                                              |
| U1       | unemployment rate of urban males 14--24                                                |
| U2       | unemployment rate of urban males 35--39                                                |
| Wealth   | wealth: median value of transferable assets or family income                           |
| Ineq     | income inequality: percentage of families earning below half the median income         |
| Prob     | probability of imprisonment: ratio of number of commitments to number of offenses      |
| Time     | average time in months served by offenders in state prisons before their first release |
| Crime    | crime rate: number of offenses per 100,000 population in 1960                          |

@@

```{r}
rf_model_v1 = randomForest(Crime ~ ., data = crime_df, ntree = 100)
rmse_func(true = crime_df$Crime, predicted=rf_model_v1$predicted)
```

```{r}
rf_model_v2 = randomForest(log(Crime) ~ ., data = crime_df, ntree = 100)
rmse_func(true = crime_df$Crime, predicted=exp(rf_model_v2$predicted))
```

```{r}
varImpPlot(rf_model_v2)
```

>>>>

| Variable | Description                                                                            |
|-------------------|-----------------------------------------------------|
| M        | percentage of males aged 14--24 in total state population                              |
| So       | indicator variable for a southern state                                                |
| Ed       | mean years of schooling of the population aged 25 years or over                        |
| Po1      | per capita expenditure on police protection in 1960                                    |
| Po2      | per capita expenditure on police protection in 1959                                    |
| LF       | labour force participation rate of civilian urban males in the age-group 14-24         |
| M.F      | number of males per 100 females                                                        |
| Pop      | state population in 1960 in hundred thousands                                          |
| NW       | percentage of nonwhites in the population                                              |
| U1       | unemployment rate of urban males 14--24                                                |
| U2       | unemployment rate of urban males 35--39                                                |
| Wealth   | wealth: median value of transferable assets or family income                           |
| Ineq     | income inequality: percentage of families earning below half the median income         |
| Prob     | probability of imprisonment: ratio of number of commitments to number of offenses      |
| Time     | average time in months served by offenders in state prisons before their first release |
| Crime    | crime rate: number of offenses per 100,000 population in 1960                          |

@@

```{r}
rf_model_v1 = randomForest(Crime ~ ., data = crime_df, ntree = 100,importance=TRUE)
rmse_func(true = crime_df$Crime, predicted=rf_model_v1$predicted)
```

```{r}
rf_model_v2 = randomForest(log(Crime) ~ ., data = crime_df, ntree = 100,importance=TRUE)
rmse_func(true = crime_df$Crime, predicted=exp(rf_model_v2$predicted))
```

```{r}
varImpPlot(rf_model_v1,sort = TRUE)
```

```{r}
rf_model_v3 = randomForest(Crime ~ . - Ineq -So -Pop, data = crime_df, ntree = 100)
rmse_func(true = crime_df$Crime, predicted=rf_model_v3$predicted)
```
